---
title: "Final project: The relationship between restaurant geographical distribution and chronic disease outcomes in New York City"
author: "Gaeun Kim(gk2501); Junting Ren(jr3755);  Leyiyu Yue(ly2428); Ruiwei Zhang(rz2375) ; "
date: "November 20, 2017"
output: 
   html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(readxl)
library(data.table)
library(stringr)
library(janitor)
library(stringr)
library(forcats)
library(jsonlite)
library(viridis)
library(plotly)
library(ggplot2)
library(knitr)
```


# Motivation---Tim

**This year, a report from Centers for Disease Control and Prevention revealed that America’s obesity rate has reached a record high. Contrasting to popular belief, New Yorkers are not so safe from the obesity epidemic, as more than half of adult New Yorkers are either overweight or obese. Studies show that the rise in the obesity epidemic is partly due to disparities in food environment; it is harder for some to eat healthier because their options are limited.**  

**For example, I and my fellow classamate often go out to McDonald that are near our home for convenience, even though these restaurants were not healthy. Environment can affect our health behaviours imperceptibly.**  

**This project intends to look deeper into the relationship between food environment in NYC and obesity rate along with diabetes rate and stroke hospitalization rate.**



# Inspiration from other related Work---Tim

**In 2008, aggregating Google search queries, Google attempted to make accurate predictions about flu activity. Then what kind of infomation on the internet that can predict the prevelence of chronic disease such as obesity, diabetes or cancer?**  

 
 
# Initial questions---Tim

**1. Can the percentage of nation-wide chain and fast-food restaurants in different neighborhood of NYC be related to their obesity, diabetes and stroke hospitalization rate ?**  

**2.Can the percentage of fast-food restaurant (defined by cuisine description in the restaurant inspection dataset) in different neighborhood of NYC be related to their obesity, diabetes and stroke hospitalization rate ?**  

**3.Can the percentage of health inspection grade A restaurant in different neighborhood of NYC be related to their obesity, diabetes and stroke hospitalization rate?**  
 
4. Can the composite restaurant health score of different neighborhood of NYC be related to their obesity, diabetes and stroke hospitalization rate?  

**For the first three questions, we stick to it. Since the percentage of health inspection grade A restaurant is not a significant predictor, we later put it into the model as a confounder. Moreover, we deleted the fourth problem. Composite restaurant health score were to subjective and difficult to assess. Moreover, we calculated the boro level model first due to the difficulties we encountered in scaping zipcode-neighborhood data. However, after some struggle, we still managed to get the neighborhood information and analyze the data accordingly.**    



# Data and Methods

## Data Source and Collection---Tim

**1. NYC restaurant inspection:**

https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j  

This dataset contains the data for restaurant inspection in NYC from August 1, 2014 to December 5th, 2017. Every row is a restaurant inspection record that includes the name of the restaurant, zipcode, cuisine type description, inspection grade (A as the best grade) and so on. Since this dataset has the inspection data for 3 years, it is almost certained that it has the data for all the restuarants in NYC in 2014.  

**Variable used in this datasets**  
DBA: Name of the restaurant  
BORO: name of the boro  
ZIPCODE: the zipcode of the restaurant  
CUISINE DESCRIPTION: the kind of food that the restaurant is providing  
GRADE: Inspection grade for the specific inspection.  

**2. 2015 Community Health Profiles Open Data: ** 

https://www1.nyc.gov/site/doh/data/data-publications/profiles.page  

This dataset contains NYC every neighborhoods' demographic (percentage of white race, poverty percentage), health (age-adjusted percent of adult exercised in the last 30 days, age-adjusted percent of adults as a smoker) and our main outcome (Age-adjusted percent of adults that is obese (BMI of 30 or gthe reater), ge-adjusted percent of adults, Age-adjusted rate of hospitalizations due to stroke (cerebrovascular disease) per 100,000 adults)

**Variable used in this datasets**  
Name: the name for the neigborhood.  
Racewhite_Rate: the percentage for white race  
Poverty: Percent of individuals living below the federal poverty threshold  
Smoking: age-adjusted percent of adults as a smoker
Exercise: Age-adjusted percent of adults that reported getting any exercise in the last 30 days  
Obesity: Age-adjusted percent of adults that is obese (BMI of 30 or greater) based on self-reported height and weight  
Diabetes: Age-adjusted percent of adults that had ever been told by a healthcare professional that they have diabetes  
Stroke_Hosp: Age-adjusted rate of hospitalizations due to stroke (cerebrovascular disease) per 100,000 adults  
  
**3. Web scraping for what zipcodes each neighborhood contains **  
Because Community Health Profiles Open Data is has only neighborhood level information, so we have to aggregate neighborhood level information from the restaurant inspeciton data. However, the restaurant inspection data was using zipcodes for every restaurant. Therefore, we had to add the neighborhood name to every restaurant, so that we can group by neighborhood then calculate the percentage for every neighborhood.   

First, we scraped the table data from https://www.health.ny.gov/statistics/cancer/registry/appendix/neighborhoods.htm. However the neighborhood name and combinations were different from the health profile data we downloaded. We cannot merge the two datasets. Then we tried to look for the raw classification for the neigborhoods in health data from New York University's Furman Center for Real Estate and Urban Policy and the NYC Department of City Planning. However, still no luck becuase the neighborhood was not divided by zipcode areas. Then we tried the hardest way: search the name of the neighborhood on Google and finding the matching zipcodes. It worked out well, but it was not precise, because neighborhoods were not divided according to the area of the zipcode. Different neighborhoods have the same zipcodes.  
**In order to be unbiased in this process, if two neighborhoods contains the same zipcode area, we will randomly assign this zipcode to only one neighborhood.**  

## Data Import and Cleaning---Tim

**Downloading restaurant inspection data from NYC open data: **

```{r reading_the_New_York_Inspection_data, message=FALSE, warning=FALSE}
get_all_inspections = function(url) {
  
  all_inspections = vector("list", length = 0)
  
  loop_index = 1
  chunk_size = 50000
  DO_NEXT = TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] = 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
                       )
          ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT = dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index = loop_index + 1
  }
  
  all_inspections
  
}

url = "https://data.cityofnewyork.us/resource/9w7m-hzhe.json"

rest_inspection = get_all_inspections(url) %>%
  bind_rows() 
```

**Downloading health and demographic data CSV into local folder and reading, cleaning it:**

```{r reading and cleaning the health indicator data}
download.file("https://www1.nyc.gov/assets/doh/downloads/excel/episrv/2015_CHP_PUD.xlsx", mode="wb", destfile = "health.xlsx")
health <- read_excel("health.xlsx", sheet = "CHP_all_data") %>% 
  select(Name, Racewhite_Rate, Poverty, Unemployment,
         Smoking, Exercise,
         Obesity, Diabetes, Stroke_Hosp) %>% 
  clean_names() 
```

**Matching the neighborhood names with restaurant zipcodes:**

```{r merging the neighborhood data with restaurant data, message=FALSE}
zip_neighbor <- read_csv("neigh_zipcode.csv") %>% 
  mutate(zipcode = as.character(zipcode))
##restaurant data with neighbourhood
rest_neighborhood = left_join(rest_inspection, zip_neighbor, by = "zipcode") %>% 
  filter(!is.na(neighborhood))
```



# Exploratory Analysis

## Health---Tim&Austin

```{r neighborhood_summary}
health_only_neighborhood <- health[-c(1:6),] %>% 
  rename(neighborhood = name) %>% 
  mutate(neighborhood = as.factor(neighborhood))
##Plotting for outcome in different neighborhood

obseity_bar_neighborhood <- health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, obesity)) %>% 
  filter(obesity > 25) %>% 
  ggplot(aes(x = neighborhood,y = obesity, fill = neighborhood)) + geom_col() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 25 percent more obesity rate")


diabetes_bar_neighborhood <- health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, diabetes)) %>% 
  filter(diabetes > 10) %>% 
  ggplot(aes(x = neighborhood,y = diabetes, fill = neighborhood)) + geom_col() +   
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 10 percent more diabetes rate")


stroke_bar_neighborhood <- health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, stroke_hosp)) %>% 
  filter(stroke_hosp > 300) %>% 
  ggplot(aes(x = neighborhood,y = stroke_hosp, fill = neighborhood)) + 
  geom_col() +    
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 300 more stroke hospitalization in 100,000 adults")

ggplotly(obseity_bar_neighborhood)
ggplotly(diabetes_bar_neighborhood)
ggplotly(stroke_bar_neighborhood)
```

**Summary: Williamsbridge and Baychester have the highest obesity rate, up to 32%. East New York and Starrett City have the highest diabetes rate, up to 17 percent. BUshwick has the highest stroke hospitalization in 100,000 adults, up to 300 adults. Morrisania and Crotona has the highest percent of poverty rate, up to 40%. Fiancial district has the highest percent of young peoeple, up to 67%.**


## Restaurant data

### Fastfood restaurants by cuisine type---Ruiwei

**Identify fastfood restaurants by their cuisine types. We print out the cuisine type list (n=85) and let everyone circle the ones they think is fastfood and we use the union as our rule (use union because it's more conservative).**

```{r calculating_percentage}
# calculating the total number of restaurants and the number of fastfood restaurants in the neighborhood, as well as the percentage of fastfood restaurants.

neighborhood_list = 
  rest_neighborhood %>%
  distinct(neighborhood) %>%
  arrange(neighborhood)
  
rest_fastfood_neighborhood = 
  rest_neighborhood %>%
  filter(cuisine_description %in% c("Bagels/Pretzels",
                                    "Bottled beverages, including water, sodas, juices, etc.",
                                    "Chicken",
                                    "Delicatessen",
                                    "Donuts",
                                    "Hamburgers",
                                    "Hotdogs",
                                    "Hotdogs/Pretzels",
                                    "Ice Cream, Gelato, Yogurt, Ices",
                                    "Nuts/Confectionary",
                                    "Pancakes/Waffles",
                                    "Pizza",
                                    "Soul Food",
                                    "Sandwiches",
                                    "Sandwiches/Salads/Mixed Buffet",
                                    "Soups & Sandwiches"))

percent_fastfood_neighborhood = function(name_neighborhood){

  rest_each_neighborhood =
    rest_neighborhood %>%
    filter(neighborhood == name_neighborhood) %>%
    distinct(camis)
  
  n_rest_neighborhood = nrow(rest_each_neighborhood)

  rest_fastfood_distinct_neighborhood = 
    rest_fastfood_neighborhood %>%
    filter(neighborhood == name_neighborhood) %>%
    distinct(camis)
  
  n_fastfood_neighborhood = nrow(rest_fastfood_distinct_neighborhood)
    
  percent_fastfood_neighborhood = n_fastfood_neighborhood/n_rest_neighborhood
  
  tibble(
    neighborhood = name_neighborhood,
    n_fastfood = n_fastfood_neighborhood,
    n_rest = n_rest_neighborhood,
    percent_fastfood = percent_fastfood_neighborhood
  )
}

fastfood_neighborhood = 
  map(neighborhood_list$neighborhood, percent_fastfood_neighborhood) %>%
  bind_rows() %>%
  mutate(neighborhood = str_to_upper(neighborhood))
```

```{r summary_neighborhood_rest}
fastfood_neighborhood %>%
  mutate(neighborhood = as.factor(neighborhood),
         n_rest = as.numeric(n_rest),
         n_nonfastfood = n_rest - n_fastfood,
         neighborhood = fct_reorder(neighborhood, percent_fastfood)) %>%
  plot_ly(., x = ~neighborhood, y = ~n_fastfood, type = 'bar', name = 'fastfood restaurants') %>%
  add_trace(y = ~n_nonfastfood, name = 'non-fastfood restaurants') %>%
  layout(yaxis = list(title = 'number of restaurants'), 
         xaxis = list(title = 'neighborhood (ordered by percentage of fastfood restaurants)',
                      tickangle = 45),
         barmode = 'stack')
```

**From the plot, we can see that, while the Greenwich Village and SOHO neighborhood has fairly large number of restaurants, it has the smallest percentage of fastfood restaurants. Williamsbridge and Baychester has the largest percentage of fastfood restaurants.**

**When large number of total restaurants is not equal to large percentage of fastfood restaurants in that neighborhood, we can conclude that the distribution of fastfood restaurants is not even across neighborhoods, which also implies the motivation of our study, we want to investigate if this uneven distribution of fastfood restaurants is associated with diffferent level of chronic disease outcomes within a neighborhood.**

### Restaurant Chains---Sara

```{r reading_rest_chains_wiki, matching_with_inspection, percentage_chains_boro}
## Matching list of chain restaurants in U.S. and restaurant inspection data

chains_html = read_html("https://en.wikipedia.org/wiki/List_of_restaurant_chains_in_the_United_States#Fast-casual")

chain_rest = chains_html %>%
  html_nodes("ul:nth-child(9) li , .jquery-tablesorter tr:nth-child(1) td:nth-child(1)") %>%
  html_text() %>%
  as.tibble() %>%
  mutate(dba = value, 
         dba = str_to_upper(dba)) %>%
  select(dba)
# read in the list of chain restaurants in us 
# made the names to uppercase and changed the var name to dba
head(chain_rest, 10)
```

**I have scraped list of 75 national chain restaurants from the wikipedia page (https://en.wikipedia.org/wiki/List_of_restaurant_chains_in_the_United_States#Fast-casual) now I will join this dataset with restaurant inspection data to choose only the chain restaurants in NYC.**

```{r joining chain and rest_neighborhood}
# removing punctuations in chain_rest & restaurant inspections (neighborhoods)
chain_rest_str = 
  chain_rest  %>%
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

rest_neigh_str = rest_neighborhood %>% 
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

# Matching the two datasets(restaurant inspection data that has all punctuation removed from dba(restaurant name) and list of chain restaurants by dba)

neighborhood_chain = 
  right_join(rest_neigh_str, chain_rest_str) %>%
  filter(!is.na(camis)) %>%
  distinct(camis, dba, neighborhood, boro)

neighborhood_chain %>%
  group_by(dba) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  head(10)
```

**The combined dataframe, nyc_chain has `nrow(nyc_chain)` observations. Also, there were 33 different chain restaurants extracted. The chart is showing the 10 chain restaurants in descending order.**

```{r chain percent calculation}
# counting chains in neighborhoods

neigh_count_chain = neighborhood_chain %>%
  group_by(neighborhood, boro) %>%
  summarise(chain_n = n())

neigh_count_rest = rest_neighborhood %>%
  distinct(neighborhood, camis) %>%
  group_by(neighborhood) %>%
  summarise(res_n = n())

# calculating percentage of chains in each boro
percent_neighborhood_chain = left_join(neigh_count_chain, neigh_count_rest) %>%
  ungroup() %>%
  mutate(chain_percentage = chain_n/res_n,
         neighborhood = str_to_upper(neighborhood))

plot_chain_neighbor = percent_neighborhood_chain %>%
  mutate(neighborhood = forcats::fct_reorder(neighborhood, chain_percentage)) %>%
  ggplot(aes(neighborhood, chain_percentage, fill = boro)) + geom_bar(stat="identity") 

ggplotly(plot_chain_neighbor)
```

I have plotted neighborhoods of NYC against their percentage of chain restaurants and grouped them by borough. We see that all the neighborhodds that had a percentage of chain restuarants less than 5% were all part of Brooklyn except Greenwhich village and Soho of Manhattan. Neighborhoods in Queens and Manhattan are spread out across low to high percentage of chain restaurants while most of neighborhoods in Bronx and Staten Island have high percentages. The neighbor hood that had the highest percentage of chain restaurants were Throgs neck and Co-op City of Bronx with 16.5% of chain restaurats out of all restaurats.

### Inspection Grade---Austin 

```{r r grade_percentage for neighborhood}
gradea_neighborhood =
  rest_neighborhood %>%
  group_by(neighborhood, grade) %>%
  summarise(n = n()) %>%
  mutate(grade_percent = n / sum(n)) %>% 
  filter(grade == "A") %>% 
  ungroup(boro) %>%
  mutate(neighborhood = str_to_upper(neighborhood))
```

```{r plot for neighborhood}
gradea_neighborhood %>% 
  mutate(neighborhood = as.factor(neighborhood),
         neighborhood = fct_reorder(neighborhood,grade_percent)) %>% 
  plot_ly(x = ~neighborhood, y = ~grade_percent, color = ~neighborhood, type = "bar")
```

**Different from the situation in borough, the difference of percentage of "grade-A" restaurants in each borough exists. "Throgs Neck and Co-op City" has the greatest grade-A restaurants percentage, around 44.50%. "Sunset Park", however, has the least, around 30.62%. "Washington Heights", where we live, takes the fourth from the end, 34.39%, which is obviously consistent with the feeling we have towards the restaurant condition of "Washington Heights".**



# Formal Analysis and Findings

## Model Selection Process

```{r getting_data_ready_for_analysis}
health_neighborhood = 
  health %>%
  mutate(neighborhood = str_to_upper(name)) %>%
  select(-name)

combined_chain = 
  percent_neighborhood_chain %>%
  select(neighborhood, chain_percentage)
combined_chain_fastfood = 
  fastfood_neighborhood %>%
  mutate(fastfood_percent = percent_fastfood) %>%
  select(neighborhood, fastfood_percent) %>%
  right_join(combined_chain, by = "neighborhood")
combined_chain_fastfood_gradea = 
  gradea_neighborhood %>%
  select(neighborhood, grade_percent) %>%
  right_join(combined_chain_fastfood, by = "neighborhood")

combined_model =  
  left_join(combined_chain_fastfood_gradea, health_neighborhood, by = "neighborhood")
```

```{r selecting_main_predictor}
outcome_name = combined_model[,10:12]

main_predictor_selection = function(outcome){

lm_fastfood =   
  lm(outcome ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() 

lm_chain =   
  lm(outcome ~ chain_percentage + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() 

lm_both =   
  lm(outcome ~ fastfood_percent + chain_percentage + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() 

lm_compare = bind_rows(lm_fastfood, lm_chain, lm_both)
}

map(outcome_name, main_predictor_selection)
```

**We originally have two main predictors of interest, *percentage of chain restaurants* and *percentage of fastfood restaurants*, and they are both significantly associated with the three chronic disease health oucomes when solely in the model after adjusting for other potential confounders. Taking obesity as example, the p-value for fastfood_percent is 0.0006801903 and for chain_percentage is 0.012419514. **

**Since we also anticipated them to be highly associated with each other, to avoid collinearity, we will need to make decision on which one to keep as the final main predictor. So we put the two predictors in the same model and see how their p-values change. As a result, the fastfood_percent stays significant (p=0.020213583) and the chain_percentage turn insignificant (p=0.651152376). **

**Thus, we keep *percentage of fastfood restaurants* (fastfood_percent) as the main predictor.**

```{r justifying_confounders}
outcome_name = combined_model[,10:12]

confounder_percent_change = function(outcome){
lm_adjusted = 
  lm(outcome ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  summary() 
lm_adjusted_tbl = 
  as.tibble(lm_adjusted[[4]]) %>%
  clean_names()

lm_crude =
  lm(outcome ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  summary() 
lm_crude_tbl = 
  as.tibble(lm_crude[[4]]) %>%
  clean_names()

percent_change = (lm_crude_tbl$estimate[2] - lm_adjusted_tbl$estimate[2]) /lm_crude_tbl$estimate[2]

confounder_percent_change = percent_change
}

map(outcome_name, confounder_percent_change)
```

**Besides some biologically meaningful covariates (i.e. race, poverty, smoking status, exercise), we also hypothesize the variable *percentage of grade A restuarants* as a potential confounder in the association between fastfood restaurants percentage and the three chronic disease health outcomes.**

**Here, we are assessing if grade_percent is a significant confounder statistically. Using the 10% change rule of thumb, we find that after adjusting for *percentage of grade A restuarants*, the estimates of fastfood_percent change by 18.83% for outcome obsesity, 3.23% for outcome diabetes and 31.72% for outcome stroke hospitalization.**

**Thus, regarding the final models, we are going to keep grade_percent for obsesity and stroke hospitalization, but take it out and rerun the model for the outcome diabetes.**

## Final Models and Findings

```{r final_model}
lm(obesity ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(diabetes ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(stroke_hosp ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()
```

<<<<<<< HEAD
## Restaurant Chains---Sara

```{r joining_Chains_neighborhood}
# removing punctuations in restaurant inspections
rest_neigh_str = rest_neighborhood %>% 
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

# Matching the two datasets(neighborhood restaurant inspection data that has all punctuation removed from dba(restaurant name) and list of chain restaurants by dba)
neighborhood_chain = 
  right_join(rest_neigh_str, chain_rest_str) %>%
  filter(!is.na(camis)) %>%
  distinct(camis, dba, neighborhood)
```

```{r chain percent calculation}
# counting chains in neighborhoods

neigh_count_chain = neighborhood_chain %>%
  group_by(neighborhood) %>%
  summarise(chain_n = n())

neigh_count_rest = rest_neighborhood %>%
  distinct(neighborhood, camis) %>%
  group_by(neighborhood) %>%
  summarise(res_n = n())

# calculating percentage of chains in each boro
percent_neighborhood_chain = left_join(neigh_count_chain, neigh_count_rest) %>%
  mutate(chain_percentage = chain_n/res_n,
         neighborhood = str_to_upper(neighborhood))

# joinining with health data
health_chain_neighborhood = left_join(percent_neighborhood_chain, health_only_neighborhood) 
```

```{r lm function}
# function for modeling health outcome and percentage of chain restaurants

lm_neighborhood = function(health_outcome){
  
 graphs_chain_health = health_chain_neighborhood %>%
  mutate(boro = forcats::fct_reorder(neighborhood, health_outcome)) %>%
  ggplot(aes(chain_percentage, health_outcome, color = neighborhood)) + geom_point() + theme(legend.position="none")
 
 reg_chain = lm(health_outcome ~ chain_percentage + racewhite_rate + age0to44_rate + poverty + smoking + exercise, data = health_chain_neighborhood) %>%
   summary()

list(graphs_chain_health, reg_chain)
# function that takes a input of column in health_chain_neighborhood and gives output of:
 
# 1. graphs_health will give a graph showing the relationship between health outcomes in neighborhoods and their percentage of chain restaurants

# 2.reg_chain gives an output of the linear regression result
}
```

```{r chain obesity regression}
lm_neighborhood(health_chain_neighborhood$obesity)

# I tried log transformation and it's even better!

#health_chain_neighborhood %>%
#  mutate(boro = forcats::fct_reorder(neighborhood, obesity)) %>%
#  ggplot(aes(chain_percentage, obesity^2, color = neighborhood)) + geom_point() + #theme(legend.position="none")
#
#lm(obesity^2 ~ chain_percentage + racewhite_rate + age0to44_rate + poverty + smoking + #exercise, data = health_chain_neighborhood) %>%
#   summary()
```

**Fitting a regression line with predictors chain_percentage, racewhite_rate, age0to44_rate, poverty,smoking, and exercise, we can see that the percentage of chains is a significant predictor with p-value, 0.01057. Holding all the other predictors constant, 62.2% increase in percentage of obesity in NYC neighborhoods is associated with 1% increase in chain restaurants. From the graph of percentage of chain restaurants and percentage of obesity, we can see there is a positive trend.**

```{r modeling neighborhood chains and diabetes}
lm_neighborhood(health_chain_neighborhood$diabetes)
```

**We can also visually see there is positive correlation between diabetes and percentage of chains. From the linear regression analysis, the results show that percentage of chain restaurants in neighborhoods is a significant predictor of percentage of diabetics in NYC neighborhoods**

```{r modeling neighborhood chains and stroke}
lm_neighborhood(health_chain_neighborhood$stroke_hosp)
```

**When fitting chain_percentage, racewhite_rate, age0to44_rate, poverty,smoking, and exercise on rate of stroke however, the outcomes indicates that chain_percentage is not a significant predictor at significance level 0.05.**  

**We have three final models each having a health outcome (prevalence of obesity, prevalence of diabetes, and stroke hospitalization rate) as the dependent variable and percentage of fastfood as the main predictor. Obesity and percentage of fastfood restuarants model gave the most significant results with p-value of the main predictor being 0.0005364 (<0.01). In other words, at significance level of 1%, every 0.1 percent increase in fastfood restaurants in a neighborhood is associated with 5% increase in the neighborhood's obesity prevalence, while adjusting for other factors.**  

**The p-value of the regression coefficients for model with outcomes as diabetes/stroke were both arround 0.003 (<0.01), indicating there is a significant linear relationship between diabetese/stroke and percentage of fastfood restaurants at 1% significance level. To put in other words, at significance level of 1%, every 1 percent increase in fastfood restaurants in a neighborhood is associated with 17.5% increase in the neighborhood's diabetes prevalence, while adjusting for other factors. Furthermore, every 1 percent increase in fastfood restaurants in a neighborhood is associated with increase in 573.5 stroke hospitalizations per 100,000 adults in the neighborhood, while adjusting for other factors.**  


**It is reasonable that among the three health outcomes, obesity has the strongest linear association with food environment, in this case, percentage of fastfood restaurants. It is a health condition that has the most direct relation with one's diet. Moreover, it has a higher prevalence than diabetes and stroke, which could lead to having a lower p-value than the other two health conditions**  

# Discussion---to do later 

**Our 2015 Community Health Profiles Open Data has data on obesity, diabetes prevalence rate from 2013 and stroke hospitalization rate from 2012. And the data of geographic distribution of restaurants is from 2014 to 2017. So the health profile data is somewhat earlier than the restaurant geographic distribution. However, as restaurant distribution and chronic disease prevalence rate wouldn’t change much over a few years, the lag between years don’t actually affect our results that much. Therefore, our results can still be valid.**  

**Although the cuisine type of a restaurant is typically assumed to directly reflect the health level of the food the restaurant provides, we demonstrated here that even the unhealthiest restaurant can offer one or several healthy food, which may bring bias to the study. This was not a low-probability event, it should have required more efficient planning to resolve. Besides, our project at first treats chain restaurants as a cutoff point for unhealthy restaurants. Obviously this cutoff point is ambiguous and farfetched. In the end, this project include this as a predictor.**  

**Lastly, although there is an association between fast-food restaurant distribution and health outcomes, we could not conclude that it is fast-food restaurant causing these health outcomes. Maybe it is because the citizens living in the neighborhood are obese indicating that they like to eat fast food. This will actually result in more fast-food restaurant opening in this neighborhood since the business will be good. Further study need to be conducted before concluding any causation effect.**  


# Conclusion---to do later 

**Overall, we conclude that there is a significant relationship between obesity/diabetes/stroke and the geographical distribution of fast-food restaurants.**



