---
title: "Final project: The relationship between restaurant geographical distribution and chronic disease outcomes in New York City"
author: "Gaeun Kim(gk2501); Junting Ren(jr3755);  Leyiyu Yue(ly2428); Ruiwei Zhang(rz2375) ; "
date: "November 20, 2017"
output: 
   html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(readxl)
library(data.table)
library(stringr)
library(janitor)
library(stringr)
library(forcats)
library(jsonlite)
library(viridis)
library(plotly)
library(ggplot2)
library(knitr)
```


# Motivation---Tim

**This year, a report from Centers for Disease Control and Prevention revealed that America’s obesity rate has reached a record high. Contrasting to popular belief, New Yorkers are not so safe from the obesity epidemic, as more than half of adult New Yorkers are either overweight or obese. Studies show that the rise in the obesity epidemic is partly due to disparities in food environment; it is harder for some to eat healthier because their options are limited. This project intends to look deeper into the relationship between food environment in NYC and obesity rate along with diabetes rate and stroke hospitalization rate.**



# Related Work---Tim

**In 2008, aggregating Google search queries, Google attempted to make accurate predictions about flu activity. Then what kind of infomation on the internet that can predict the prevelence of chronic disease such as obesity, diabetes or cancer?**  

**Another inspiration is that, I and my fellow classamate often go out to restaurants that are near our home for convenience, even though these restaurants were not healthy. Environment can affect some health behaviours imperceptibly.**

 
 
# Initial questions---Tim

**1. Can the percentage of certain fast-food restaurant be related to obesity, diabetes and stroke rate in different neighborhoods of NYC?** 

**2. Can the percentage of health inspection grade A restaurant be related to obesity, diabetes and stroke rate in different neighborhoods of NYC?** 

**3. Can the composite restaurant health score of each neighborhood be related to chronic disease rate?**

**For the first two questions, we stick to it. For the third question, we change the main predictor to percentage of fast food cuisine type since it was easy to acquire in the data. Composite restaurant health score were to subjective and difficult to assess. Moreover, we calculated the boro level model first due to the difficulties we encountered in scaping zipcode-neighborhood data. However, after some struggle, we still managed to get the neighborhood information and analyze the data accordingly.**



# Data and Methods

## Data Source and Collection---Tim

**1. NYC restaurant inspection:**

https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j 

**2. 2015 Community Health Profiles Open Data: ** 

https://www1.nyc.gov/site/doh/data/data-publications/profiles.page
  
**These data were rather easy to acquire, since they can be downloaded by CSV format. Because health and demographic data are grouped by neighborhood but the restaurant inspection data was using zipcodes. We had to match the zipcode and neighborhood name in order to merge the datasets which was the hardest.** 

**First, we scraped the table data from https://www.health.ny.gov/statistics/cancer/registry/appendix/neighborhoods.htm. However the neighborhood name and combinations were different from the health profile data we downloaded. We cannot merge the two datasets. Then we tried to look for the raw classification for the neigborhoods in health data from New York University's Furman Center for Real Estate and Urban Policy and the NYC Department of City Planning. However, still no luck becuase the neighborhood was not divided by zipcode areas. Then we tried the hardest way: search the name of the neighborhood on Google and finding the matching zipcodes. It worked out well, but it was not precise, thus we left out some of the restaurants without a matching neighborhood name.**


## Data Import and Cleaning---Tim

**Downloading restaurant inspection data from NYC open data: **

```{r reading_the_New_York_Inspection_data, message=FALSE, warning=FALSE}
get_all_inspections = function(url) {
  
  all_inspections = vector("list", length = 0)
  
  loop_index = 1
  chunk_size = 50000
  DO_NEXT = TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] = 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
                       )
          ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT = dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index = loop_index + 1
  }
  
  all_inspections
  
}

url = "https://data.cityofnewyork.us/resource/9w7m-hzhe.json"

rest_inspection = get_all_inspections(url) %>%
  bind_rows() 
```

**Downloading health and demographic data CSV into local folder and reading, cleaning it:**

```{r reading and cleaning the health indicator data}
download.file("https://www1.nyc.gov/assets/doh/downloads/excel/episrv/2015_CHP_PUD.xlsx", mode="wb", destfile = "health.xlsx")
health <- read_excel("health.xlsx", sheet = "CHP_all_data") %>% 
  select(Name, Racewhite_Rate, Age0to17_rate, 
         Age18to24_rate, Age25to44_rate, Poverty, Unemployment,
         Smoking, Exercise,
         Obesity, Diabetes, Stroke_Hosp) %>% 
  clean_names() %>% 
  mutate(age0to44_rate = age0to17_rate + age18to24_rate + age25to44_rate) %>% 
  select(-age0to17_rate, -age18to24_rate, -age25to44_rate)
  
```

**Matching the neighborhood names with restaurant zipcodes:**

```{r merging the neighborhood data with restaurant data, message=FALSE}
zip_neighbor <- read_csv("neigh_zipcode.csv") %>% 
  mutate(zipcode = as.character(zipcode))
##restaurant data with neighbourhood
rest_neighborhood = left_join(rest_inspection, zip_neighbor, by = "zipcode") %>% 
  filter(!is.na(neighborhood))
```



# Exploratory Analysis

## Health---Tim&Austin

```{r neighborhood_summary}
health_only_neighborhood <- health[-c(1:6),] %>% 
  rename(neighborhood = name) %>% 
  mutate(neighborhood = as.factor(neighborhood))
##Plotting for outcome in different neighborhood


health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, obesity)) %>% 
  filter(obesity > 25) %>% 
  ggplot(aes(x = neighborhood,y = obesity, fill = neighborhood)) + geom_col() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 25 percent more obesity rate")


health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, diabetes)) %>% 
  filter(diabetes > 10) %>% 
  ggplot(aes(x = neighborhood,y = diabetes, fill = neighborhood)) + geom_col() +   
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 10 percent more diabetes rate")


health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, stroke_hosp)) %>% 
  filter(stroke_hosp > 300) %>% 
  ggplot(aes(x = neighborhood,y = stroke_hosp, fill = neighborhood)) + 
  geom_col() +    
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") +
  labs(title = "Neighborhood with 300 more stroke hospitalization in 100,000 adults")



##Plotting for some adjusted variables


health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, poverty)) %>% 
  filter(poverty > 20) %>% 
  ggplot(aes(x = neighborhood,y = poverty, fill = neighborhood)) + geom_col() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none") +
  labs(title = "Neighborhood with 20 percent or more poverty")


health_only_neighborhood %>%
  mutate(neighborhood = fct_reorder(neighborhood, age0to44_rate)) %>% 
  filter(age0to44_rate > 60) %>% 
  ggplot(aes(x = neighborhood,y = age0to44_rate, fill = neighborhood)) + 
  geom_col() +    
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none") +
  labs(title = "Neighborhood with 60 percent or more people under age 44")


```

**Summary: Williamsbridge and Baychester have the highest obesity rate, up to 32%. East New York and Starrett City have the highest diabetes rate, up to 17 percent. BUshwick has the highest stroke hospitalization in 100,000 adults, up to 300 adults. Morrisania and Crotona has the highest percent of poverty rate, up to 40%. Fiancial district has the highest percent of young peoeple, up to 67%.**


## Restaurant data

### Fastfood restaurants by cuisine type---Ruiwei

```{r identifying_fastfood_cuisine_type, eval=FALSE}
# Identify fastfood restaurants by their cuisine types. We print out the cuisine type list (n=85) and let everyone circle the ones they think is fastfood and we use the union as our rule (use union because it's more conservative).

rest_inspection %>%
  mutate(dba = str_to_upper(dba)) %>%
  arrange(cuisine_description) %>%
  count(cuisine_description)
```

```{r calculating_percentage}
# calculating the total number of restaurants and the number of fastfood restaurants in the neighborhood, as well as the percentage of fastfood restaurants.

neighborhood_list = 
  rest_neighborhood %>%
  distinct(neighborhood) %>%
  arrange(neighborhood)
  
rest_fastfood_neighborhood = 
  rest_neighborhood %>%
  filter(cuisine_description %in% c("Bagels/Pretzels",
                                    "Bottled beverages, including water, sodas, juices, etc.",
                                    "Chicken",
                                    "Delicatessen",
                                    "Donuts",
                                    "Hamburgers",
                                    "Hotdogs",
                                    "Hotdogs/Pretzels",
                                    "Ice Cream, Gelato, Yogurt, Ices",
                                    "Nuts/Confectionary",
                                    "Pancakes/Waffles",
                                    "Pizza",
                                    "Soul Food",
                                    "Sandwiches",
                                    "Sandwiches/Salads/Mixed Buffet",
                                    "Soups & Sandwiches"))

percent_fastfood_neighborhood = function(name_neighborhood){

  rest_each_neighborhood =
    rest_neighborhood %>%
    filter(neighborhood == name_neighborhood) %>%
    distinct(camis)
  
  n_rest_neighborhood = nrow(rest_each_neighborhood)

  rest_fastfood_distinct_neighborhood = 
    rest_fastfood_neighborhood %>%
    filter(neighborhood == name_neighborhood) %>%
    distinct(camis, cuisine_description)
  
  n_fastfood_neighborhood = nrow(rest_fastfood_distinct_neighborhood)
    
  percent_fastfood_neighborhood = n_fastfood_neighborhood/n_rest_neighborhood
  
  tibble(
    neighborhood = name_neighborhood,
    n_fastfood = n_fastfood_neighborhood,
    n_rest = n_rest_neighborhood,
    percent_fastfood = percent_fastfood_neighborhood
  )
}

fastfood_neighborhood = 
  map(neighborhood_list$neighborhood, percent_fastfood_neighborhood) %>%
  bind_rows() %>%
  mutate(neighborhood = str_to_upper(neighborhood))
```

```{r summary_neighborhood_rest}
fastfood_neighborhood %>%
  mutate(neighborhood = as.factor(neighborhood),
         n_rest = as.numeric(n_rest),
         n_nonfastfood = n_rest - n_fastfood,
         neighborhood = fct_reorder(neighborhood, percent_fastfood)) %>%
  plot_ly(., x = ~neighborhood, y = ~n_fastfood, type = 'bar', name = 'fastfood restaurants') %>%
  add_trace(y = ~n_nonfastfood, name = 'non-fastfood restaurants') %>%
  layout(yaxis = list(title = 'number of restaurants'), 
         xaxis = list(title = 'neighborhood (ordered by percentage of fastfood restaurants)',
                      tickangle = 45),
         barmode = 'stack')
```

**From the plot, we can see that, while the Greenwich Village and SOHO neighborhood has fairly large number of restaurants, it has the smallest percentage of fastfood restaurants. Williamsbridge and Baychester has the largest percentage of fastfood restaurants.**

**When large number of total restaurants is not equal to large percentage of fastfood restaurants in that neighborhood, we can conclude that the distribution of fastfood restaurants is not even across neighborhoods, which also implies the motivation of our study, we want to investigate if this uneven distribution of fastfood restaurants is associated with diffferent level of chronic disease outcomes within a neighborhood.**

### Restaurant Chains---Sara

```{r reading_rest_chains_wiki, matching_with_inspection, percentage_chains_boro}
## Matching list of chain restaurants in U.S. and restaurant inspection data

chains_html = read_html("https://en.wikipedia.org/wiki/List_of_restaurant_chains_in_the_United_States#Fast-casual")

chain_rest = chains_html %>%
  html_nodes("ul:nth-child(9) li , .jquery-tablesorter tr:nth-child(1) td:nth-child(1)") %>%
  html_text() %>%
  as.tibble() %>%
  mutate(dba = value, 
         dba = str_to_upper(dba)) %>%
  select(dba)
# read in the list of chain restaurants in us 
# made the names to uppercase and changed the var name to dba
head(chain_rest, 10)
```

**I have scraped list of 75 national chain restaurants from the wikipedia page (https://en.wikipedia.org/wiki/List_of_restaurant_chains_in_the_United_States#Fast-casual) now I will join this dataset with restaurant inspection data to choose only the chain restaurants in NYC.**

```{r joining chain and rest_inspection}
# removing punctuations in chain_rest & restaurant inspections
chain_rest_str = 
  chain_rest  %>%
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

rest_inspect_str = rest_inspection %>% 
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

# Matching the two datasets(restaurant inspection data that has all punctuation removed from dba(restaurant name) and list of chain restaurants by dba)
nyc_chain = 
  right_join(rest_inspect_str, chain_rest_str) %>%
  filter(!is.na(camis)) %>%
  distinct(camis, dba, boro)

nyc_chain %>%
  group_by(dba) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  head(10)
```

**The combined dataframe, nyc_chain has `nrow(nyc_chain)` observations. Also, there were 33 different chain restaurants extracted. The chart is showing the 10 chain restaurants in descending order.**

```{r joining_Chains_neighborhood}
# removing punctuations in restaurant inspections
rest_neigh_str = rest_neighborhood %>% 
  mutate(dba = str_replace_all(dba, "[[:punct:]]", ""))

# Matching the two datasets(neighborhood restaurant inspection data that has all punctuation removed from dba(restaurant name) and list of chain restaurants by dba)
neighborhood_chain = 
  right_join(rest_neigh_str, chain_rest_str) %>%
  filter(!is.na(camis)) %>%
  distinct(camis, dba, neighborhood, boro)
```

```{r chain percent calculation}
# counting chains in neighborhoods

neigh_count_chain = neighborhood_chain %>%
  group_by(neighborhood, boro) %>%
  summarise(chain_n = n())

neigh_count_rest = rest_neighborhood %>%
  distinct(neighborhood, camis) %>%
  group_by(neighborhood) %>%
  summarise(res_n = n())

# calculating percentage of chains in each boro
percent_neighborhood_chain = left_join(neigh_count_chain, neigh_count_rest) %>%
  ungroup() %>%
  mutate(chain_percentage = chain_n/res_n,
         neighborhood = str_to_upper(neighborhood))

plot_chain_neighbor = percent_neighborhood_chain %>%
  mutate(neighborhood = forcats::fct_reorder(neighborhood, chain_percentage)) %>%
  ggplot(aes(neighborhood, chain_percentage, fill = boro)) + geom_bar(stat="identity") 

ggplotly(plot_chain_neighbor)
```

I have plotted neighborhoods of NYC against their percentage of chain restaurants and grouped them by borough. We see that all the neighborhodds that had a percentage of chain restuarants less than 5% were all part of Brooklyn except Greenwhich village and Soho of Manhattan. Neighborhoods in Queens and Manhattan are spread out across low to high percentage of chain restaurants while most of neighborhoods in Bronx and Staten Island have high percentages. The neighbor hood that had the highest percentage of chain restaurants were Throgs neck and Co-op City of Bronx with 16.5% of chain restaurats out of all restaurats.

### Inspection Grade---Austin 

```{r r grade_percentage for neighborhood}
gradea_neighborhood =
  rest_neighborhood %>%
  group_by(neighborhood, grade) %>%
  summarise(n = n()) %>%
  mutate(grade_percent = n / sum(n)) %>% 
  filter(grade == "A") %>% 
  ungroup(boro) %>%
  mutate(neighborhood = str_to_upper(neighborhood))
```

```{r plot for neighborhood}
gradea_neighborhood %>% 
  mutate(neighborhood = as.factor(neighborhood),
         neighborhood = fct_reorder(neighborhood,grade_percent)) %>% 
  plot_ly(x = ~neighborhood, y = ~grade_percent, color = ~neighborhood, type = "bar")
```

**Different from the situation in borough, the difference of percentage of "grade-A" restaurants in each borough exists. "Throgs Neck and Co-op City" has the greatest grade-A restaurants percentage, around 44.50%. "Sunset Park", however, has the least, around 30.62%. "Washington Heights", where we live, takes the fourth from the end, 34.39%, which is obviously consistent with the feeling we have towards the restaurant condition of "Washington Heights".**



# Formal Analysis and Findings

## Model Selection Process

```{r getting_data_ready_for_analysis}
health_neighborhood = 
  health %>%
  mutate(neighborhood = str_to_upper(name)) %>%
  select(-name)

combined_chain = 
  percent_neighborhood_chain %>%
  select(neighborhood, chain_percentage)
combined_chain_fastfood = 
  fastfood_neighborhood %>%
  mutate(fastfood_percent = percent_fastfood) %>%
  select(neighborhood, fastfood_percent) %>%
  right_join(combined_chain, by = "neighborhood")
combined_chain_fastfood_gradea = 
  gradea_neighborhood %>%
  select(neighborhood, grade_percent) %>%
  right_join(combined_chain_fastfood, by = "neighborhood")

combined_model =  
  left_join(combined_chain_fastfood_gradea, health_neighborhood, by = "neighborhood")
```

```{r selecting_main_predictor}
lm(obesity ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(obesity ~ chain_percentage + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(obesity ~ fastfood_percent + chain_percentage + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()
```

**We originally have two main predictors of interest, *percentage of chain restaurants* and *percentage of fastfood restaurants*, and they are both significantly associated with the three chronic disease health oucomes when solely in the model after adjusting for other potential confounders. Taking obesity as example, the p-value for fastfood_percent is 0.0006801903 and for chain_percent is 0.012419514.**

**We will need to make decision on which to keep as the final main predictor. So we put the two predictors in the same model and **

****

```{r justifying_confounders}
lm(diabetes ~ fastfood_percent + grade_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()
lm(diabetes ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()
```

## Final Models and Findings

```{r final_model}
lm(obesity ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(diabetes ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()

lm(stroke_hosp ~ fastfood_percent + racewhite_rate + poverty + smoking + exercise, combined_model) %>%
  broom::tidy() %>%
  kable()
```



# Conclusion---to do later 

write



# Discussion---to do later 

write





